---
title: "Titanic"
output: html_document
---
##Content

    Introduction

    1.1 Objective

    1.2 Data Understanding

    Data Preparation and Exploratory Analysis

    2.1 Data Cleaning

    2.2 Exploratory Analysis and Data Processing

    Modeling

    3.1 Feature Engineering

    3.2 Model Training

    3.3 Model Evaluation

    Prediction
##Introduction
  
  1.1 Objective

The sinking of the RMS Titanic is one of the most infamous shipwrecks in history. On April 15, 1912, during her maiden voyage, the Titanic sank after colliding with an iceberg, killing 1502 out of 2224 passengers and crew. This sensational tragedy shocked the international community and led to better safety regulations for ships.

One of the reasons that the shipwreck led to such loss of life was that there were not enough lifeboats for the passengers and crew. Although there was some element of luck involved in surviving the sinking, some groups of people were more likely to survive than others, such as women, children, and the upper-class.

In this challenge, we are going to complete the analysis of what sorts of people were likely to survive.
1.2 Data Understanding

To download data, click here

The data has been split into two groups:

    training set (train.csv)
    test set (test.csv)

The training set is used to build machine learning models. For the training set, we provide the outcome (also known as the “ground truth”) for each passenger. Your model will be based on “features” like passengers’ gender and class. You can also use feature engineering to create new features.

The test set should be used to see how well your model performs on unseen data. For the test set, we do not provide the ground truth for each passenger. It is your job to predict these outcomes. For each passenger in the test set, use the model you trained to predict whether or not they survived the sinking of the Titanic.

##Data Dictionary

Variable 	 Definition    	Key
survival 	- Survival   	    0 = No, 1 = Yes
pclass 	 -  Ticket class  	1 = 1st, 2 = 2nd, 3 = 3rd
sex     -	 Sex 	
Age 	  -   Age in years 	
sibsp   -  	# of siblings / spouses aboard the Titanic 	
parch 	-   # of parents / children aboard the Titanic 	
ticket 	   Ticket number 	
fare 	  - s  Passenger fare 	
cabin     - 	Cabin number 	
embarked  -	Port of Embarkation 	C = Cherbourg, Q = Queenstown, S = Southampton

##Variable Notes

pclass: A proxy for socio-economic status (SES) 1st = Upper 2nd = Middle 3rd = Lower

age: Age is fractional if less than 1. If the age is estimated, is it in the form of xx.5

sibsp: The dataset defines family relations in this way... Sibling = brother, sister, stepbrother, stepsister Spouse = husband, wife (mistresses and fiancés were ignored)

parch: The dataset defines family relations in this way... Parent = mother, father Child = daughter, son, stepdaughter, stepson Some children travelled only with a nanny, therefore parch=0 for them.

First, let's load the data and take a look at it.

```{r}
library('dplyr') # data manipulation
library('ggplot2') # Data Visualization
library('ggthemes') # Data Visualization
Titanic = read.csv("train.csv")
Test = read.csv("test.csv")
Test$Survived <- NA
```

```{r }
#Structure of Titanic dataset
str(Titanic)
```
```{r}
summary(Titanic)
```
```{r}
head(Titanic)
```
We've got a sense of our variables, their class type, and the first few observations of each. We know we're working with 1309 observations of 12 variables. In which 891 observations are from train data set, and 418 observations are from test data set. When separate the variables by type, we have ordinal variable PassengerId, lable variable Name and Ticket, numeric variables such as Age, SibSp, Parch, Fare, and categorical variables like Survived ,Pclass, Sex ,Cabin, and Embarked.

##2. Data Preparation and Exploratory Analysis
 
2.1 Data Cleaning

 From the data set, we notice that there are missing values in Age, Cabin ,Fare and Embarked column. We are going to replace missing values in Age with a random sample from        existing ages. For Cabin, since cabin number makes little sense to the result, we are going to create a new Cabin column to indicate how many cabins the passenger has.
 
#Age:
```{r}
#Missing values in dataset,we create the function which NA values replace by median values of ages in Train and Test dataset
Titanic$Age <- ifelse(is.na(Titanic$Age), mean(Titanic$Age, na.rm=TRUE), Titanic$Age)
Test$Age <- ifelse(is.na(Test$Age), mean(Test$Age, na.rm=TRUE), Test$Age)
summary(Test)
```
#Fare
```{r}
# check missing
Test$PassengerId[is.na(Test$Fare)]
Test[1044,]
```
#Embarked
```{r}
summary(Titanic$Embarked)
embarked <- Titanic$Embarked
n = length(embarked)
for(i in 1:n){
  if(embarked[i] != "S" && embarked[i] != "C" && embarked[i] != "Q"){
    embarked[i] = "S"
  }
}
table(embarked)
```

2.1 Exploratory Analysis and Data Processing

As our objective is to figure out what features would influence the survival, we are going to go deep into the data to explore the relationship between each attribute and survival.
#Age vs Survival
```{r}
#Age between 20 year and 40 year are high  survived rate and Elder peoples have low survival rate
ggplot(Titanic, aes(Age,fill = factor(Survived))) +
    geom_histogram()+ theme(legend.position="top")+ylab("Frequency")
```

#SEX vs Survival
```{r}
#Male has low survival rate than Female.Female survived more than Male
ggplot(Titanic, aes(Sex,fill = factor(Survived))) +    geom_histogram(stat = "count")+ylab("Frequency")
```

```{r}
#Survival Rate 
tapply( Titanic$Survived,Titanic$Sex, mean)
```
The survival rate of female is 0.74, while the survival rate of male is 0.18.
#Embarked vs Survived
```{r}
ggplot(Titanic, aes(Embarked,fill = factor(Survived))) + geom_histogram(stat = "count")
```
#Pclass vs Survived
```{r}
ggplot(Titanic, aes(Pclass,fill = factor(Survived))) +  geom_histogram(stat = "count")
```
#Fare vs Survived
```{r}
ggplot(Titanic, aes(Fare,fill = factor(Survived))) +  geom_histogram()
```
```{r}

```

```{r}
ggplot(Titanic, aes(Parch,fill = factor(Survived))) +  geom_histogram(stat = "count")
```
```{r}
ggplot(Titanic, aes(SibSp,fill = factor(Survived))) +  geom_histogram(stat = "count")
```

##LOGISTIC REGRESSION MODAL
```{r}
full=bind_rows(Titanic,Test)
train=full[1:891,]
test=full[892:1309,]

```
##Logit
```{r}
rf_model=glm(factor(Survived)  ~ Pclass + Age + Fare + Embarked, data = train ,family="binomial" )

rf_result=predict(rf_model, test,type="response")
rf_result = as.numeric(rf_result > 0.5)
table(rf_result, Test$Survived)
rf_solution = data.frame(PassengerId = test$PassengerId, Survived = rf_result)

write.csv(rf_solution, file = "submissions.csv", row.names = F)
```


